\documentclass[a4paper,10pt]{article}
\usepackage[left=1cm, right=1cm, top=1cm, bottom=1cm]{geometry}
\usepackage{xcolor, enumitem, hyperref}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{fontawesome5}

% Define Colors
\definecolor{primary}{RGB}{40, 44, 52}
\definecolor{secondary}{RGB}{220, 220, 220}

\titleformat{\section}{\color{primary}\large\bfseries}{}{0em}{}[\color{primary}\titlerule]

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Anmol Mathur}} \\
    {\large Technology Leader | CTO | Architect} \\
    \href{mailto:anmolm@gmail.com}{anmolm@gmail.com} | +91 - 9867191999 | \href{https://www.anmolmathur.com}{www.anmolmathur.com} | \href{https://linkedin.com/in/anmolmathur}{LinkedIn} 
\end{center}

\vspace{5mm}

% Summary
\section*{Profile}
Technology leader with 23+ years of experience, including 15 years in banking and financial services. Proven track record in identifying, qualifying, and implementing enabling technologies and enterprise systems that drive strategic objectives. Deep expertise in digital transformation, cost optimization, and managing large technology teams across multiple geographies.

% Skills
\section*{Expertise}
\begin{itemize}[leftmargin=0.5cm]
    \item Banking Technology Leadership
    \item Digital Transformation \& Cloud Computing
    \item IT Cost and Infra Management
    \item System Architecture and Infrastructure Design
    \item Leadership \& Team Management
    \item Multi-Cloud Optimization (AWS/GCP/Azure)
    \item Vendor Management
    \item Full Project Life Cycle Management
\end{itemize}

% Experience
\section*{Work Experience}
\textbf{Head Technology \\ VP Engineering} \hfill \textit{Hungama Digital Media Entertainment} \\
Mumbai | June 2023 - Present
\begin{itemize}[leftmargin=0.5cm]
    \item Lead the Technology Department for Hungama Digital’s portfolio of brands.
    \item Digitally transformed the Technology Stack into Kubernetes using CNCF Technologies.
    \item Reduced Technology Opex by over 50\% (from 3Cr to 1.4Cr).
    \item Implemented organizational AI strategy through Trypromptly no-code platform.
    \item Manage 66+ member Technology Team while ensuring SLAs of 98\%+ uptime.
\end{itemize}

\textbf{VP IT Development} \hfill \textit{Hong Kong \\ Shanghai Bank (HSBC)} \\
Mumbai and Hong Kong | Aug 2008 - Jan 2016
\begin{itemize}[leftmargin=0.5cm]
    \item Managed the receivables business software for HSBC's corporate banking division across multiple regions.
    \item Led implementation of Intellect NNC for Cash Management Business, integrating with core HSBC systems.
    \item Oversaw the Alternate Delivery Channel (ADC) portfolio for Retail Banking, including ATM networks, Internet Banking, and Call Centers.
    \item Successfully implemented the Automatic Clearing House (ACH) proposition for India and Core Banking System Improvement Programs.
    \item Partnered with cross-functional teams: Network, Desktop, Software Development, Operations, Compliance, IT Security, Finance.
\end{itemize}

\textbf{Project Manager / Business Analyst} \hfill \textit{Oracle Financial Services} \\
Mumbai and New York | Dec 2001 - Aug 2008
\begin{itemize}[leftmargin=0.5cm]
    \item Managed Global Cash Management Software (GCMS) implementation for Citibank.
    \item Led teams of 12-25 for development and implementation across multiple phases.
    \item Designed funding and user profile modules for Citigroup’s cash management systems.
    \item Worked as a Technical Developer and Application Designer for Citigroup projects including Sapphire, GPOS, and CitiDirect using Java/J2EE/Oracle Technology.
\end{itemize}

\textbf{Technology Leadership Roles} \hfill \textit{Various Companies} \\
\begin{itemize}[leftmargin=0.5cm]
    \item Head Technology & VP Engineering, Times Professional Learning (TimesPro) (Sep 2021 - Mar 2023)
    \item Technology Director, Xfinite Technologies (Mzaalo) (Jan 2020 - Aug 2021)
    \item Technology Director & Head Outsourcing, Digitas India (Client - Formula 1) (Dec 2016 - Jan 2020)
    \item Chief Technology Officer (CTO), Ogaan Media (Elle & SquareInch) (Jan 2016 - Dec 2016)
\end{itemize}

% Technical Domains
\section*{Technical Expertise}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Banking Systems:} Core Banking, Receivables Management, Cash Management, Trade Finance
    \item \textbf{Financial Channels:} ATM, Internet Banking, Mobile Banking, Call Centers
    \item \textbf{Cloud Platforms:} AWS, GCP, Azure, Websphere, APIGEE
    \item \textbf{Programming:} Java, PHP, Python, Ruby On Rails, NodeJS, ReactJS, VueJS
    \item \textbf{Data Management:} SQL, NoSQL, Big Data, Big Query, Tableau, Power BI
\end{itemize}

% International Exposure
\section*{International Exposure}
\begin{itemize}[leftmargin=0.5cm]
    \item New York, USA – 1 year
    \item London, UK – 4 months
    \item Hong Kong, China – 4 months
\end{itemize}

% Education
\section*{Education}
\textbf{Michigan State University} \hfill 2021 \\
Effective Leadership and Management Certification

\textbf{NMIMS, University of Mumbai} \hfill 2004-2008 \\
MBA, Marketing

\textbf{VESIT, University of Mumbai} \hfill 1997-2001 \\
Bachelor of Engineering (B.E), Electronics

% Languages
\section*{Languages}
\begin{itemize}[leftmargin=0.5cm]
    \item English
    \item Hindi
\end{itemize}

% Footer
\vfill
\begin{center}
    \footnotesize \textit{Last updated: \today}
\end{center}

\end{document}
